---
title: "Run Targets - Landsat Collection 2 SR/ST Acquisition"
date: "`r Sys.Date()`"
author: "ROSSyndicate"
output:
  html_document: default
  pdf_document: default
---

# Purpose

This is a helper script that loads all necessary packages to run the targets 
pipeline, then runs it to acquire Landsat Collection 2 surface reflectance and
surface temperature for user-defined areas of interest (AOI).

## Install necessary packages

```{r package_installer, echo = F}
package_installer <- function(x) {
  if (x %in% installed.packages()) {
    print(paste0('{', x ,'} package is already installed.'))
    } else {
      install.packages(x)
      print(paste0('{', x ,'} package has been installed.'))
    }
  }
```

List packages that need to be checked for install, and walk the function along them all.

```{r walk_package_installer, message = F}
packages <- c('tidyverse',
              'reticulate',
              'targets',
              'tarchetypes',
              'yaml',
              'nhdplusTools',
              'polylabelr',
              'sf')

lapply(packages, package_installer)
```

## Authenticate and initialize Earth Engine

You will need to have [installed and initialized the `gcloud CLI`](https://cloud.google.com/sdk/docs/install) 
and have a [Google Earth Engine account](https://code.earthengine.google.com/register) 
prior to running this workflow. Some common troubleshooting solutions 
[can be found here]<https://github.com/rossyndicate/ROSS_RS_mini_tools/blob/main/helps/CommonIssues.md>).

### Authentication

To authenticate your GEE account, we will use a Python environment created in the 
R file 'data_acquisition/src/py/pySetup.R'. This will take a few minutes if you 
haven't yet run the python setup script while it creates a virtual environment.

```{r}
source('data_acquisition/py/pySetup.R')
```

### Authenticate your instance of GEE

```{python}
import ee

ee.Authenticate(auth_mode = 'localhost')
```

## Run the targets pipeline and output a network graph.

Prior to running this pipeline, you'll need to populate the `config.yml` file 
with the information for the Landsat Surface Reflectance and Surface Temperature 
Collection 2 product stack pull. Additionally, you will need to change line 5 of 
the `_targets.R` file if you have renamed the config file from `config.yml`.

```{r run_targets, echo = F}
library(targets)

{
  tar_make()
  
  tar_visnetwork()
}
```


